Jeff Goldsmith

### 2018-10-22 papers.Rmd
small update to check github ...

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2018+).
Nonlinear mixed-effects models for PET data.
<i> Transactions on Biomedical Engineering, </i> 
accepted.

@@

P. T. Reiss, **J. Goldsmith**, H. L. Shang, and R. T. Ogden.
Methods for Scalar-on-Function Regression (2017).
<i> International Statistical Review, </i>
<b>85</b> 228-249.

@@

T. Kitago<sup>&#8224;</sup>, **J. Goldsmith**<sup>&#8224;</sup>, M. Harran, L. Kane, J. Berard, S. Huang, S. Ryan, P. Mazzoni, J, Krakauer, and V. Huang (2015).
Robotic therapy for chronic stroke: general recovery of impairment or improved task-specific skill?
<i> Journal of Neurophysiology, </i>
<b>114</b> 1885-1894.
[[Link](http://jn.physiology.org/content/early/2015/07/10/jn.00336.2015.abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26032276)]
(&#8224; denotes equal contribution)

>>>>

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2018+).
Nonlinear mixed-effects models for PET data.
<i> Transactions on Biomedical Engineering, </i> 
accepted.
[[Link](https://ieeexplore.ieee.org/document/8424003/)]

@@

P. T. Reiss, **J. Goldsmith**, H. L. Shang, and R. T. Ogden.
Methods for Scalar-on-Function Regression (2017).
<i> International Statistical Review, </i>
<b>85</b> 228-249.
[[Link](https://onlinelibrary.wiley.com/doi/abs/10.1111/insr.12163)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28919663)]

@@

T. Kitago<sup>&#8224;</sup>, **J. Goldsmith**<sup>&#8224;</sup>, M. Harran, L. Kane, J. Berard, S. Huang, S. Ryan, P. Mazzoni, J, Krakauer, and V. Huang (2015).
Robotic therapy for chronic stroke: general recovery of impairment or improved task-specific skill?
<i> Journal of Neurophysiology, </i>
<b>114</b> 1885-1894.
[[Link](http://jn.physiology.org/content/early/2015/07/10/jn.00336.2015.abstract)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/26180120)]
(&#8224; denotes equal contribution)
